Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-03 paper/paper.qmd
commit changes to paper.qmd

### Predictive Variables
The predictive variables is 'state' 
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-state-distribution
#| fig-cap: "Bar plot showing the distribution of observations across key battleground states in the 2024 United States Presidential Election polling data. The plot illustrates the count of polling observations for each state, highlighting states with more frequent polling activity. This visualization aids in understanding the level of engagement and data collection in each battleground state leading up to the election."

# Visualize the distribution of the state variable
ggplot(clean_poll_data, aes(x = state)) +
  geom_bar(fill = "steelblue") +  # Bar plot with specified fill color
  labs(
    title = "Distribution of State Variable in Polling Data",
    x = "State",
    y = "Count of Observations"
  ) +
  theme_minimal() +  # Use a minimal theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )
```

Another predictive variable is 'end-date'
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-end-date-distribution
#| fig-cap: "Histogram illustrating the distribution of polling end dates for key battleground states in the lead-up to the 2024 United States Presidential Election. The histogram shows the frequency of polls conducted over time, providing insight into the timing of polling activities and potential trends in voter sentiment as Election Day approaches. This visualization is crucial for understanding how polling data correlates with the election timeline."

>>>>

### Predictive Variables
#### State
The state variable indicates the U.S. state where the poll was conducted or targeted. In the context of the U.S. presidential election, the outcome is frequently determined by several key states. In the current 2024 election cycle, there are seven battleground states that are pivotal in the contest between Kamala Harris, representing the Democratic Party, and Donald Trump, representing the Republican Party. To enhance our model and refine our predictions, we focused exclusively on these seven battleground states. The polling results from each of these states play a crucial role in predicting electoral outcomes, as the percentage of support is evaluated on a state-by-state basis.
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-state-distribution
#| fig-cap: "Bar plot showing the distribution of observations across key battleground states in the 2024 United States Presidential Election polling data. The plot illustrates the count of polling observations for each state, highlighting states with more frequent polling activity. This visualization aids in understanding the level of engagement and data collection in each battleground state leading up to the election."

# Visualize the distribution of the state variable
ggplot(clean_poll_data, aes(x = state)) +
  geom_bar(fill = "steelblue") +  # Bar plot with specified fill color
  labs(
    title = "Distribution of State Variable in Polling Data",
    x = "State",
    y = "Count of Observations"
  ) +
  theme_minimal() +  # Use a minimal theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )
```
The distribution of the state variable is visualized in @fig-state-distribution and indicates that some states, such as Pennsylvania, North Carolina and Wisconsin have more polling observations compared to others, like Nevada. This variability reflects differences in polling frequency and interest among these battleground states. States with more polling observations provide a larger sample size, potentially leading to more stable and reliable predictions for those states in the model.

#### End Date
Another predictive variable is 'end-date'
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-end-date-distribution
#| fig-cap: "Histogram illustrating the distribution of polling end dates for key battleground states in the lead-up to the 2024 United States Presidential Election. The histogram shows the frequency of polls conducted over time, providing insight into the timing of polling activities and potential trends in voter sentiment as Election Day approaches. This visualization is crucial for understanding how polling data correlates with the election timeline."
